\documentclass[10pt,letterpaper,roman]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.75, left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{import}

\name{Jeff}{Martin}
%\title{Resume}
\address{100 Institute Road, Worcester MA, 01609}{}{}
\phone[mobile]{1 (207) 281-3406}
\social[linkedin]{www.linkedin.com/in/jeff-a-martin/}
\social[github]{www.github.com/Jeff-A-Martin}
\email{jamartin@wpi.edu}

\begin{document}
    \makecvtitle
    \vspace{-0.5in}
    \begin{center}
        \small{Undergraduate student of Computer Science seeking admission to a graduate program in Cognitive Artificial Intelligence or Machine Learning for the fall of 2018.}
    \end{center}
        
    \vspace{-0.25in}

    \section{Education}
        
        \cventry{2015--Present}{Bachelor of Science in Computer Science, Class of 2019}{Worcester Polytechnic Institute}{Worcester, MA}{GPA: 3.98/4.00}{\textit{Minor in Electrical and Computer Engineering}}{}
        
        \begin{itemize}
            \item{\textbf{Relevant Coursework}: Algorithms, AI, SWE, Machine Learning*, Data Mining*, Secure SWE*, \\OOD, Database Systems, Numerical Methods of Analysis*.} 
            \item{\textbf{Programming Languages}: Java, C, Scala, Python, SQL, HTML, CSS}
            \item{\textbf{Software and Systems}: Git, \LaTeX, Linux}
        \end{itemize}


    \vspace{-0.1in}

    \section{Work Experience}
        \cventry{May 2017--August 2017}{Cyber Analytics and Decision Systems, Research Intern}{MIT Lincoln Laboratory}{Lexington, MA}{}{
            \begin{itemize}
                \item{Developed a taxonomy for cyber security data visualization tools by conducting an extensive literature review.} 
                \item{Implemented analysis features in an existing cyber security data visualization tool using Scala.}
                \item{Designed and implemented infrastructure to support the streaming of large time-stamped datasets using Java.} 
            \end{itemize}}
        
        \cventry{July 2016--August 2016}{Software Engineer Intern}{Analog Devices Incorporated}{Wilmington, MA}{}{
            \begin{itemize}
                \item{Implemented Bluetooth communication infrastructure to support an internet of things project.}
                \item{Designed a custom Bluetooth Low Energy protocol to maximize the rate of data transfer.}
                \item{Implemented \textit{server} infrastructure to transmit data from an embedded device using C.}
                \item{Implemented \textit{client} infrastructure to receive transmitted data for Android and Linux systems using Java and Python.}
            \end{itemize}}

    \vspace{-0.1in}

    \section{Project Experience}
        \cventry{August 2017--October 2017}{Major Qualifying Project (Senior Capstone) }{Cyber Security Data Analysis Framework for Advanced Persistent Threat Detection}{WPI}{}{
            \begin{itemize}
                \item{Collaborated with two students to develop a data analysis tool for the detection of advanced persistent cyber security threats.}
                \item{Implemented infrastructure with Java to support the insertion, partitioning, classification, and aggregation of large cyber security datasets; designed the framework to support an ensemble of the classifiers and visualization the dataset.}
                \item{Implemented a random forest and neural network to detect anomalous events in authentication records using Python and Java.}
            \end{itemize}} 
        
        \cventry{August 2016--October 2016}{Artificial Intelligence (\textit{CS4341})}{Rubik's Cube Solver}{WPI}{}{
            \begin{itemize}
                \item{Designed a novel Rubik's Cube solver that employed the IDA* search algorithm and sub-goal decomposition.}
                \item{Implemented the solver with the Manhattan Distance heuristic and multiple decompositions using Java.} \item{Performed a experiment to measure the performance of each decomposition.}
                \item{Refined the solver to be 33\% more move-efficient and 93\% more time-efficient than an average human solver.}
            \end{itemize}} 

    \vspace{-0.1in}    

    \section{Leadership Experience}        
        \cventry{2015--Present}{Vice President (\textit{Current}),Webmaster (\textit{Current}), President, Treasurer, Secretary}{Institute of Electrical and Electronics Engineers}{WPI}{}{} 
 
        \cventry{August 2016--Present}{Senior Assistant (\textit{Tutor})}{Computer Science Department}{WPI}{}{}
      
        \cventry{August 2016--May 2017}{Residential Advisor}{Residential Services}{WPI}{}{}

    \vspace{0.1in}
   
    \textit{*To be completed by May of 2018.}
\end{document}
